Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-17 Papers/ms.tex
Simulated data image
Horseshoe image

\section{Simulated Data}
To demonstrate the method, we generated a simulated dataset with a single
substructure. The image is shown in Figure X.

\section{The Cosmic Horseshoe}
As a demonstration the method is the applied to the Cosmic Horseshoe INT data. 
The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens. This model is has been used often  \cite{Dye2008}, \cite{schneider_falcoa_Ehlers_1994},      . 
The second model has in addition to the flexible source and SIE, also possible satellites. \\
The amount of added satellites is automatically determined by the program. If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.  \\
In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\

>>>>

\section{Simulated Data}
To demonstrate the method, we generated a simulated dataset with a single
substructure. The image is shown in Figure~\ref{fig:simulated_image}.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{simulated_image.pdf}
\caption{\label{fig:simulated_image}}
\end{center}
\end{figure}

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the X-band INT
image of the Cosmic Horseshoe \citep{}, which is shown in
Figure~\ref{fig:horseshoe_image}.

%The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
%The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens. This model is has been used often  \cite{Dye2008}, \cite{schneider_falcoa_Ehlers_1994},      . 
%The second model has in addition to the flexible source and SIE, also possible satellites. \\
%The amount of added satellites is automatically determined by the program. If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.  \\
%In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{horseshoe_image.pdf}
\caption{\label{fig:horseshoe_image}}
\end{center}
\end{figure}
